A Spatial AR System for Wide-area Axis-aligned Augmentation of Planar Scenes in Industrial Settings

### 2021-06-22 paper/elsarticle/elsarticle-template.tex
paper

>>>>

A natural extension of this work would be to extend it to handle planar and non-planar scenes alike. To handle non-planar scenes would call for a change in how scene geometry is recovered and how distortion of the image to be projected is carried out; projector calibration---presented here as a one-time step---could, however, remain unchanged.
